%!TEX root = ../../../main.tex

\subsection{Context}

This report has been developed during an internship at Antares Lda. and as part of the course unit Project/Internship (PESTI), Bachelor's in Informatics Engineering at Polytechnic of Porto - School of Engineering (ISEP). It covers the development process of a software solution and it's results, targeting hyper parameter optimization as part of the training process of machine learning algorithms.

Antares Lda. (and it's parent company FARO Technologies), is a key player in the 3D measurement, imaging and realization market, producing a large variety of devices (from contact and non-contact measurement arms to laser scanners) and a suite software solutions to integrate FARO's devices into any customer's workflow (CAM2\texttrademark and others). (CITE WEBSITE)
 
Machine learning (GLOSSARY HERE) is an evergrowing field (CITE INCREASE IN MACHINE LEARNING), with uses in both commercial and academic situations. As such, every process in it's development process has been a subject to a large amount of research (from new model development to improvements in training and deployment technologies) (CITE INCREASE IN MACHINE LEARNING RESEARCH).

One of the most important and impactful areas of research in the ML (GLOSSARY HERE) is hyper parameter optimization (FIND CITATION FOR IMPACTFULLNESS OF HPO(glossary?). This process targets the training process of machine learning algorithms, defining the training steps structure and execution (FIND CITATION FOR THIS).